Compositional Verification of Concurrent C Programs with Search Structure Templates

### 2023-09-18 concurrency/CPP 2024/paper.tex
link zenodo for artifact
rephrase flow interface mention in intro

Our specific contributions are:
\begin{itemize}
	\item We reimplement the template approach without flow interfaces, with a simple interface involving only the concept of ``keys belonging in this node/subtree''.
	\item We implement the template approach in VST, allowing us to apply it to C programs and obtain end-to-end correctness proofs in a single verification system.
	\item To the best of our knowledge, this is the first mechanized verification of a template approach to concurrent data structure implementations in a real-world programming language, and its first application to data structures not written specifically as case studies.
	\item We give a precise description of search structure templates, and identify places where it is difficult in practice to preserve the boundary between template and data structure.
\end{itemize}

>>>>

Our specific contributions are:
\begin{itemize}
	\item We reimplement the template approach independently of flow interfaces, with a simple interface involving only the concept of ``keys belonging in this node/substructure''.
	\item We implement the template approach in VST, allowing us to apply it to C programs and obtain end-to-end correctness proofs in a single verification system.
	\item To the best of our knowledge, this is the first mechanized verification of a template approach to concurrent data structure implementations in a real-world programming language, and its first application to data structures not written specifically as case studies.
	\item We give a precise description of search structure templates, and identify places where it is difficult in practice to preserve the boundary between template and data structure.
\end{itemize}
